The Assembly of Black Hole Mass ad Luminosity Functions of High-redshift Quasars\\via Multiple Accretion Episodes

### 2022-09-30 ms.tex
.

%%%%%%%
%    Fig. 7
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=85mm]{LF_spreadz7.pdf}\hspace{2mm}
\includegraphics[width=85mm]{LF_spreadz8.pdf}\\\vspace{5mm}
\includegraphics[width=85mm]{LF_spreadz9.pdf}\hspace{2mm}
\includegraphics[width=85mm]{LF_spreadz10.pdf}
\caption{
The predicted quasar luminosity functions at (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, (d) $z\sim 10-13$.
The black solid and dashed curves are the unobscured and intrinsic QLF, respectively, and the shaded region presents the $1\sigma$ statistical error.
The expected depths and volumes of future surveys with Wide Euclid (blue; $YJH=23$ mag) and Wide RST (red; $YJH=27$ mag) are overlaid in each panel (see Table~\ref{tab:N_detect}).
For comparison, the galaxy UV luminosity functions are plotted with the data points (grey) and the fitting functions in purple with a Schechter (dotted) and double power-law (dash-dotted) shape.
The luminosity function data are taken from \citet{2013MNRAS.432.2696M}, \citet{2016ApJ...819..129O}, \citet{2018ApJ...867..150M},
\citet{2019ApJ...883...99S}, \citet{2020MNRAS.493.2059B}, \citet{2021AJ....162...47B},
\citet{2022ApJS..259...20H,Harikane_2022b,Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2022arXiv220709434N}.
The fitting forms of the galaxy luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.}
\label{fig:LFs}
\vspace{5mm}
\end{figure*}

@@

We overlay the expected depths and survey volumes of upcoming near-infrared surveys by
Euclid (\citealt{2011arXiv1110.3193L}; \citealt{2019Barnett}) and RST \citep{2019arXiv190205569A}.
We here consider only their wide-area survey layers because narrow-field deep surveys are not suitable for high-$z$ quasars \citep[but see][]{2022arXiv220907325O}.
\blue{
Table~\ref{tab:N_detect} summarizes the expected number of quasars from those surveys.
We first integrate the QLFs at the apparent magnitude $m_{1450}\leq$ 24 mag and 27 mag for Euclid and RST, respectively.
These depths are the 5$\sigma$ point source detection limits in the $YJH$ bands of the two facilities.
}
Euclid will cover $\simeq 100-700$ quasars at $z\sim7-8$ down to the limiting magnitude, and can reach up to $z\sim 9$.
The RST will explore fainter ($\Muv>-22$ mag) and more abundant quasar populations up to $z\sim 10$.
% and increase the detection number by a factor of $\sim 2-6$ depending on the redshift range.
% However, realistic detection numbers are reduced from those ideal ones when we take into account selection criteria to differentiate 
% high-$z$ quasars from other astrophysical sources such as Galactic brown dwarfs and low-$z$ galaxy interlopers.
However, the estimated values above give upper bounds of the number of detectable high-$z$ quasars,
because selection completeness is not unity in the selection of high-$z$ quasars.
\citet{2019Barnett} investigated the efficiency of quasar selection with Euclid images and
\blue{found that combined with ground-based optical observations,
$z\sim 7-9$ quasars can be identified down to $J \sim$ 23 mag}
due to photometric noise and contaminants in the color selection such as Galactic brown dwarfs and low-$z$ early-type galaxies.
Adopting $YJH=23$ mag as the effective depth, %based on the quasar selection methods for Euclid \citep{2019Barnett},
our predicted detection numbers are in good agreement with their results but shows a better match for the case
where the QLFs are extrapolated with $10^{-0.72z}$ toward higher redshfits
(see the fourth column in their Table~3).

>>>>

%%%%%%%
%    Fig. 7
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=85mm]{LF_spreadz7.pdf}\hspace{2mm}
\includegraphics[width=85mm]{LF_spreadz8.pdf}\\\vspace{5mm}
\includegraphics[width=85mm]{LF_spreadz9.pdf}\hspace{2mm}
\includegraphics[width=85mm]{LF_spreadz10.pdf}
\caption{
The predicted quasar luminosity functions at (a) $z\sim 7$, (b) $z\sim 8$, (c) $z\sim 9$, (d) $z\sim 10-13$.
The black solid and dashed curves are the unobscured and intrinsic QLF, respectively, and the shaded region presents the $1\sigma$ statistical error.
The expected depths and volumes of future surveys with Wide Euclid (blue; $m_{1450}= 23$ mag) and Wide RST (red; $m_{1450}= 27$ mag) are overlaid in each panel (see Table~\ref{tab:N_detect}).
For comparison, the galaxy UV luminosity functions are plotted with the data points (grey) and the fitting functions in purple with a Schechter (dotted) and double power-law (dash-dotted) shape.
The luminosity function data are taken from \citet{2013MNRAS.432.2696M}, \citet{2016ApJ...819..129O}, \citet{2018ApJ...867..150M},
\citet{2019ApJ...883...99S}, \citet{2020MNRAS.493.2059B}, \citet{2021AJ....162...47B},
\citet{2022ApJS..259...20H,Harikane_2022b,Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2022arXiv220709434N}.
The fitting forms of the galaxy luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.}
\label{fig:LFs}
\vspace{5mm}
\end{figure*}

@@

We overlay the expected depths and survey volumes of upcoming near-infrared surveys by
Euclid (\citealt{2011arXiv1110.3193L}; \citealt{2019Barnett}) and RST \citep{2019arXiv190205569A}.
We here consider only their wide-area survey layers because narrow-field deep surveys are not suitable for high-$z$ quasars \citep[but see][]{2022arXiv220907325O}.
\blue{
Table~\ref{tab:N_detect} summarizes the expected number of quasars from those surveys.
We first integrate the QLFs at the apparent magnitude $m_{1450}\leq$ 24 mag and 27 mag for Euclid and RST, respectively.
These depths are the 5$\sigma$ point source detection limits in the $YJH$ bands of the two facilities.
}
Euclid will cover $\simeq 100-700$ quasars at $z\sim7-8$ down to the limiting magnitude, and can reach up to $z\sim 9$.
The RST will explore fainter ($\Muv>-22$ mag) and more abundant quasar populations up to $z\sim 10$.
% and increase the detection number by a factor of $\sim 2-6$ depending on the redshift range.
% However, realistic detection numbers are reduced from those ideal ones when we take into account selection criteria to differentiate 
% high-$z$ quasars from other astrophysical sources such as Galactic brown dwarfs and low-$z$ galaxy interlopers.
However, the estimated values above give upper bounds of the number of detectable high-$z$ quasars,
because selection completeness is not unity in the selection of high-$z$ quasars.
\citet{2019Barnett} investigated the efficiency of quasar selection with Euclid images and
\blue{found that combined with ground-based optical observations,
$z\sim 7-9$ quasars can be identified down to $J \sim$ 23 mag}
due to photometric noise and contaminants in the color selection such as Galactic brown dwarfs and low-$z$ early-type galaxies.
Adopting $m_{1450}=23$ mag as the effective depth, %based on the quasar selection methods for Euclid \citep{2019Barnett},
our predicted detection numbers are in good agreement with their results but shows a better match for the case
where the QLFs are extrapolated with $10^{-0.72z}$ toward higher redshfits
(see the fourth column in their Table~3).
